\disstitle

### 2018-06-13 chapters/introduction/introduction.tex
further improvement

%Outline:
\begin{itemize}
  \item sliver bullet and ``summer project'' story
  \item Geometry is important.
  \item traditional method for geometry detection
  \item deep learning (gamer changer)
  \item geometry detection with deep learning
  \item geometry for deep learning training
  \item overhead images
\end{itemize}

@@

In the area of vanishing point detection, we are among the first
researches that use deep neural networks to solve the problem. The
deep neural networks prove to be a good tool to extract high-level
information that offer great help to conquer the problems in camera
geometry estimation. \todo{many citations}.
%
\newline \newline
%
In computer vision, low-level elements like edges, line segments,
super-pixels and vanishing points play important roles in many
applications like image measuration, facade detection, and
geo-localization.
Though the CNNs are good at extracting high-level information from
images, more and more researches start focusing on using CNN to
extract low-level these elements.
%
Lee \etal~\cite{lee2017semantic} propose to detect semantic line
segments, which are able to segment the scene semantically, using
neural network. Maninis \etal~\cite{maninis2016convolutional} and Yang
\etal~\cite{yang2016object} explore to detect object contours with
CNNs.
%
Aside from edges and contours, another category of low-level
information that the CNNs can detect is the camera geometry, like
camera location, vanishing points, and horizon lines.
Zhai \etal~\cite{zhai2016horizon} Firstly try to detect horizon
line and vanishing point using global image context extracted by CNN.
Workman \etal~\cite{workman2016horizon} take the idea further and
design an end-to-end network to predict horizon line from images
in the wild. 
Hold-Geoffroy \etal~\cite{hold2017perceptual}
improve~\cite{workman2016horizon}'s results by using deeper networks,
and introduce a new perceptual measure for horizon line detection.
Unlike the previous work that mainly focus on horizon line detection,
Zhang \etal~\cite{zhang2018dominant} propose to detect the dominant
vanishing point using deep neural networks.

>>>>

%Outline:
\begin{itemize}
  \item sliver bullet and ``summer project'' story
  \item \st{Geometry is important.}
  \item \st{traditional method for geometry detection}
  \item \st{deep learning (gamer changer)}
  \item \st{geometry detection with deep learning}
  \item geometry for deep learning training
  \item overhead images
\end{itemize}

@@

In computer vision, low-level elements like edges, line segments,
super-pixels and vanishing points play important roles in many
applications like image measuration, facade detection, and
geo-localization.
Though the CNNs are good at extracting high-level information from
images, more and more researches start focusing on using CNN to
extract low-level these elements.
%
Lee \etal~\cite{lee2017semantic} propose to detect semantic line
segments, which are able to segment the scene semantically, using
neural network. Maninis \etal~\cite{maninis2016convolutional} and Yang
\etal~\cite{yang2016object} explore to detect object contours with
CNNs.
%
Aside from edges and contours, another category of low-level
information that the CNNs can detect is the camera geometry, like
camera location, vanishing points, and horizon lines.
%
In the area of vanishing point detection, we are among the first
researches that use deep neural networks to solve the problem. The
deep neural networks prove to be a good tool to extract high-level
information that offer great help to conquer the problems in camera
geometry estimation. \todo{many citations}.
%
